Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2014-10-26 Papers/InProgress/LogicAndReligionCongress/Abstract.tex
Minor cosmetic changes

Nevertheless, \citet[p.~7]{Hajek2002} (in page 7) acknowledges Anderson's rebuttal, and apparently accepts it, as evidenced by  his use\footnote{
  A4 and A5 are used by \citet[p.~11]{Hajek2002} (page 11) in the proofs of, respectively, Lemma 4 and Theorem 4.
} 
of A4 and A5, as well as varying domain semantics, in his new
emendation (named \AOEH \citep[sec.~4]{Hajek2002}, cf. Appendix
\ref{apx:Hajek1}), which replaces Anderson's A:A1 and A2 by a simpler
axiom H:A12. Surprisingly, the computer-assisted formalization of
\AOEH\ shows that A4 and A5 are still superfluous (not needed for proving T3). Moreover, A4 and A5 are independent\footnote{
  An axiom $A$ is \emph{independent} of a set of axioms $S$ iff there are models of $S$ where $A$ is true and other models of $S$ where $A$ if false. 
} of the other axioms and definitions. Therefore, A4 and A5 are not redundant, despite their superfluousness.

@@

Nevertheless, \AOEHH\ is explicitly regarded by \citet[p.~12]{Hajek2002} (page 12) as just an intermediary step towards a more natural theory, based on a more sophisticated notion of positiveness. That is his final emendation (\AOEHHH, cf. \ref{apx:Hajek3}), which restores A3 and does use A4 and A5, albeit in a modified form (i.e. H:A4 and H:A5). The formalization of \AOEHHH\ shows that H:A4 is independent. The old A5 is independent as well, and both H:A4 and H:A5 are superfluous, but no conclusive results were achieved regarding independence or redundancy of H:A5.

>>>>

Nevertheless, \citet[p.~7]{Hajek2002} acknowledges Anderson's rebuttal, and apparently accepts it, as evidenced by  his use\footnote{
  A4 and A5 are used by \citet[p.~11]{Hajek2002} (page 11) in the proofs of, respectively, Lemma 4 and Theorem 4.
} 
of A4 and A5, as well as varying domain semantics, in his new
emendation (named \AOEH \citep[sec.~4]{Hajek2002}, cf. Appendix
\ref{apx:Hajek1}), which replaces Anderson's A:A1 and A2 by a simpler
axiom H:A12. Surprisingly, the computer-assisted formalization of
\AOEH\ shows that A4 and A5 are still superfluous (not needed for proving T3). Moreover, A4 and A5 are independent\footnote{
  An axiom $A$ is \emph{independent} of a set of axioms $S$ iff there are models of $S$ where $A$ is true and other models of $S$ where $A$ if false. 
} of the other axioms and definitions. Therefore, A4 and A5 are not redundant, despite their superfluousness.

@@

Nevertheless, \AOEHH\ is explicitly regarded by \citet[p.~12]{Hajek2002} as just an intermediary step towards a more natural theory, based on a more sophisticated notion of positiveness. That is his final emendation (\AOEHHH, cf. \ref{apx:Hajek3}), which restores A3 and does use A4 and A5, albeit in a modified form (i.e. H:A4 and H:A5). The formalization of \AOEHHH\ shows that H:A4 is independent. The old A5 is independent as well, and both H:A4 and H:A5 are superfluous, but no conclusive results were achieved regarding independence or redundancy of H:A5.
